\textbf{Computational Fuzzy Extractors}

### 2013-04-03 trunk/CompFuzzExt.tex
Switched HILL imp to relaxed HILL

\newcommand{\metric}{\ensuremath{\mathtt{Metric}}\xspace}
\newcommand{\hill}{\ensuremath{\mathtt{HILL}}\xspace}
\newcommand{\yao}{\ensuremath{\mathtt{Yao}}\xspace}
\newcommand{\unp}{\ensuremath{\mathtt{unp}}\xspace}
\newcommand{\metricstar}{\ensuremath{\mathtt{Metric}^*}\xspace}
\newcommand{\metricd}{\ensuremath{\mathtt{Metric}^*\mathtt{-d}}\xspace}
\newcommand{\hillstar}{\ensuremath{\mathtt{HILL}^*}\xspace}
\newcommand{\hillprime}{\ensuremath{\mathtt{HILL'}}\xspace}
\newcommand{\metricprime}{\ensuremath{\mathtt{Metric'}}\xspace}
\newcommand{\metricprimestar}{\ensuremath{\mathtt{Metric'}^*}\xspace}
\newcommand{\hillprimestar}{\ensuremath{\mathtt{HILL'}^*}\xspace}
\newcommand{\poly}{\ensuremath{\mathtt{poly}}\xspace}
\newcommand{\rank}{\ensuremath{\mathtt{rank}}\xspace}
\newcommand{\ngl}{\ensuremath{\mathtt{ngl}}\xspace}
\newcommand{\Hoo}{\mathrm{H}_\infty}
\newcommand{\Hav}{\tilde{\mathrm{H}}_\infty}
\newcommand{\Dom}{\mathsl{Dom}}
\newcommand{\Range}{\mathsl{Rng}}
\newcommand{\Keys}{\mathsl{Keys}}
\def\col{\mathrm{Col}}

@@

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
We recall a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}, as extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}.

\begin{definition}
Let $(X, Z)$ be a pair of random variables.  $X$ has 
\emph{conditional HILL entropy} at least $k$ conditioned on $Z$,
denoted $H^{\hill}_{\epsilon, s_{sec}}(X|Z)\geq k$ if there exists a collection of
distributions $Y_z$ for each $z\in Z$, giving rise to a joint distribution
$(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((X, Z),(Y,Z))\leq \epsilon$.
\end{definition}

\lnote{is there any reason we can't work for the more relaxed notion of HILL, where the condition can be changed, too?}Intuitively, conditional HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  However, as we show in Section~\ref{sec:imp HILL sketch}, such secure sketches cannot  perform much better than the information-theoretic ones. \lnote{this paragraph needs rephrasing and better gluing with the next one}

%Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.  This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  
%  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.

Suppose we redefine secure sketches using HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$. 
Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches). For the Hamming metric, our result essentially matches the bound on information-theoretic secure sketches of \cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  In fact, we show that, for the Hamming metric, HILL-entropy secure sketches imply information-theoretic ones with similar parameters, and, therefore, the HILL relaxation gives no advantage.

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.  In order to have  $H^{\hill}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y$ such that $\Hav(Y | \sketch(W))\geq \tilde{m}$ and $(Y, \sketch(W))$ is computationally indistinguishable from $(W, \sketch(W))$.  Sample a sketch $s\leftarrow \sketch(W)$. We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).  So, by indistinguishability, it must also succeed on $Y$: specifically, $\rec (y',s) = y$ with high probability, for $y\leftarrow Y|s$ and $y'\leftarrow B_t(y)$).
 This means we can construct a large set $C$ from the support of $Y|s$.  $C$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.

@@

Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword. \lnote{is there a source we can reference for the terms average-error and maximal-error?}\bnote{I think the right thing to reference is Cover-Thomas, but I don't have a copy to check right now}

 \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
\end{definition}
An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.  We use the following pruning argument from Cover and Thomas~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We can now formalize the intuition above.  A sketch that retains $\tilde{m}$-bits of HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{sam}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Let $s_{rec}$ denote the size of the circuit that computes $\rec$.  If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

@@

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $Y_s$ be a collection of distributions over $\mathcal{M}$ giving rise to $Y$ such that $\Hav(Y | \sketch(W))\geq k$ and
\[ 
\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, \sketch(W)))<\epsilon.
\]  
where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $Y$ must exist by the definition of conditional HILL entropy.
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $z\in\mathcal{M}, s \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem  $z'\leftarrow \sample(z, t')$.
\subitem If $\rec(z', s) \neq  z$ output $0$.
\item Output $1$.
\end{enumerate}
 By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
$\delta^D((Y, \sketch(W)), (Y, \sketch(W)))<\epsilon$, we know $\Pr[D(Y, \sketch(W)) = 1]>1-\epsilon-t\delta$.  By Markov's inequality,  there exists a set $S_W$ such that $\Pr[\sketch(W)\in S_W]\ge 1/2$ and for all $s\in \sketch(W)$, $\Pr[ D(Y_s, s) =1]> 1- 2(\epsilon + t\delta)$.  Moreover, by \cite[Lemma 2.2a]{DBLP:journals/siamcomp/DodisORS08} (which is derived simply via Markov's inequality applied to the positive random variable $\max_y \Pr[Y_s=y]$), there exists a set $S'_W$ such that $\Pr[\sketch(W)\in S'_W]> 1/2$ and for all $s\in \sketch(W)$, $\Hoo(Y_s)\ge k-1$. \lnote{simplified this derivation}\bnote{I don't believe this fix}  Fix one value $s \in S_W\cap S'_W$ (which exists because the sum of probabilities of $S_W$ and $S'_W$ is greater than 1).  
Thus, for all such that $t', 1\leq t'\leq t$, 
\[ \Pr_{y\leftarrow Y_s}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]> 1-2(\epsilon+t\delta).\]  
%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
Thus,  $Y$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,s)$.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
\end{proof}

@@

\ignore{
\subsection{Old parameter setting}
The question then becomes whether there is a setting 
Our construction has two goals: 1) maximizing correcting capability~(while retaining polynomial time decoding, and 2) maximizing the unpredictability entropy of $W$ conditioned on the construction~($\tilde{m}$ in \defref{def:comp secure sketch}).  Our parameters will differ significantly depending on what setting of $t$ is used.  We will consider both settings where $t\leq m/n-1$ and $t\leq c\log n (m/n-1)$.  Recall these corresponding to Construction~\ref{cons:decoding algorithm} running either in fixed polynomial time or time approximately $n^{2c}$.  We consider each of these settings:

>>>>

\newcommand{\metric}{\ensuremath{\mathtt{Metric}}\xspace}
\newcommand{\hill}{\ensuremath{\mathtt{HILL}}\xspace}
\newcommand{\hillrlx}{\ensuremath{\mathtt{HILL-rlx}}\xspace}
\newcommand{\yao}{\ensuremath{\mathtt{Yao}}\xspace}
\newcommand{\unp}{\ensuremath{\mathtt{unp}}\xspace}
\newcommand{\metricstar}{\ensuremath{\mathtt{Metric}^*}\xspace}
\newcommand{\metricd}{\ensuremath{\mathtt{Metric}^*\mathtt{-d}}\xspace}
\newcommand{\hillstar}{\ensuremath{\mathtt{HILL}^*}\xspace}
\newcommand{\hillprime}{\ensuremath{\mathtt{HILL'}}\xspace}
\newcommand{\metricprime}{\ensuremath{\mathtt{Metric'}}\xspace}
\newcommand{\metricprimestar}{\ensuremath{\mathtt{Metric'}^*}\xspace}
\newcommand{\hillprimestar}{\ensuremath{\mathtt{HILL'}^*}\xspace}
\newcommand{\poly}{\ensuremath{\mathtt{poly}}\xspace}
\newcommand{\rank}{\ensuremath{\mathtt{rank}}\xspace}
\newcommand{\ngl}{\ensuremath{\mathtt{ngl}}\xspace}
\newcommand{\Hoo}{\mathrm{H}_\infty}
\newcommand{\Hav}{\tilde{\mathrm{H}}_\infty}
\newcommand{\Dom}{\mathsl{Dom}}
\newcommand{\Range}{\mathsl{Rng}}
\newcommand{\Keys}{\mathsl{Keys}}
\def\col{\mathrm{Col}}

@@

\subsection{Bounds on Secure Sketches using HILL entropy}
\label{sec:imp HILL sketch}
HILL entropy is a commonly used computational notion of entropy \cite{DBLP:journals/siamcomp/HastadILL99}.  It was extended to the conditional case by Hsiao, Lu, Reyzin~\cite{DBLP:conf/eurocrypt/HsiaoLR07}, here we recall a weaker definition due to Gentry and Wichs~\cite{gentry2011separating}~(the term relaxed HILL entropy was introduced in~\cite{reyzin2011some}).

\begin{definition}
Let $(W, X)$ be a pair of random variables.  $W$ has 
\emph{relaxed HILL entropy} at least $k$ conditioned on $X$,
denoted $H^{\hill-rlx}_{\epsilon, s_{sec}}(W|X)\geq k$ if there exists a joint distribution $(Y, Z)$, such that $\tilde{H}_\infty(Y|Z)\geq k$ and $\delta^{\mathcal{D}_{s_{sec}}} ((W, X),(Y,Z))\leq \epsilon$.
\end{definition}

%\lnote{is there any reason we can't work for the more relaxed notion of HILL, where the condition can be changed, too?}

Intuitively, HILL entropy is as good as average min-entropy for all computationally-bounded observers.  Thus, redefining secure sketches using HILL entropy is a  natural relaxation of the original information-theoretic definition; in particular, the construction in \lemref{lem:fuzzy ext construction} would yield pseudorandom outputs if the secure sketch ensured high HILL entropy.  
%Instead, in \secref{sec:unp secure sketch}, we relax the definition by allowing by outputting a new random variable that can be recovered when $\dis (w, w')\leq t$.  This object is the computational analogue of a fuzzy conductor~\cite{KanukurthiR09}.%This is a noisy computational conductor define computational secure sketches using unpredictability, and work with that definition for the rest of the paper.  
%  In \secref{sec:comp fuzzy extractors}, we show that computational fuzzy extractors can be constructed from  computational fuzzy conductors.
%The size of the circuits becomes important, we would like the \rec procedure to be computable by a circuit significantly smaller than the \hill entropy circuit size.  We simply include both of these parameters in the definition.  We review other definitions of computational entropy in Appendix~\ref{sec:notionsEntropy}.
We will consider secure sketches that retain relaxed HILL entropy: that is, we say that $(\sketch, \rec)$ is a  \emph{HILL-entropy~$(\mathcal{M}, m, \tilde{m}, t)$ secure sketch} that is $(\epsilon,s_{sec})$-hard with error $\delta$ if it satisfies \defref{def:secure sketch}, with the security requirement replaced by $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\geq \tilde{m}$.

Unfortunately, we will show below that such a secure sketch implies an error correcting code with approximately $2^{\tilde{m}}$ points that can correct $t$ random errors (see  \cite[Lemma C.1]{DBLP:journals/siamcomp/DodisORS08} for a similar bound on information-theoretic secure sketches). For the Hamming metric, our result essentially matches the bound on information-theoretic secure sketches of \cite[Proposition 8.2]{DBLP:journals/siamcomp/DodisORS08}.  In fact, we show that, for the Hamming metric, HILL-entropy secure sketches imply information-theoretic ones with similar parameters, and, therefore, the HILL relaxation gives no advantage.

The intuition for building error-correcting codes from HILL-entropy secure sketches is as follows.  In order to have  $H^{\hillrlx}_{\epsilon, s_{sec}}(W|\sketch(W))\ge \tilde{m}$, there must be a distribution $Y, Z$ such that $\Hav(Y | Z)\geq \tilde{m}$ and $(Y, Z)$ is computationally indistinguishable from $(W, \sketch(W))$.  Sample a sketch $s\leftarrow \sketch(W)$. We know that $\sketch$ followed by $\rec$ likely succeeds on $W|s$  (i.e., $\rec (w', s) = w$ with high probability for $w\leftarrow W|s$ and $w'\leftarrow B_t(w)$).  %So, by indistinguishability, it must also succeed on $Y$. 
 Consider the following experiment: 1) sample $z\leftarrow Z$, 2) draw $y\leftarrow Y|z$ and 3) $y'\leftarrow B_t(y)$. By indistinguishability $\rec (y',z) = y$ with high probability.
 This means we can construct a large set $C$ from the support of $Y|z$.  $C$ will be an error correcting code and $\rec$ an efficient decoder.  We can then use standard arguments to turn this code into an information theoretic sketch.

@@

Shannon codes work for all codewords. We can also consider a formulation that works for an ``average'' codeword.

 \begin{definition}
Let $C$ be a distribution over space $\mathcal{M}$.  We say that $C$ is an $(t,\epsilon)$-\emph{average error Shannon code} if there exists an efficient procedure $\rec$ such that for all $t'\le t$
$\Pr_{c\leftarrow C}[\rec(\sample(c, t')) \neq c]<\epsilon$.
\end{definition}
An average error Shannon code is one whose average probability of error is bounded by $\epsilon$.  See~\cite[Pages 192-194]{cover2006elements} for definitions of average and maximal error probability.  An average-error Shannon code is convertible to a maximal-error Shannon code with a small loss.  We use the following pruning argument from~\cite[Pages 202-204]{cover2006elements} (we provide a proof in \secref{sec:proof of average to maximal error}):
\begin{lemma}
\label{lem:averageToMaximalError}
Let $C$ be a $(t, \epsilon)$-average error Shannon code with recovery procedure $\rec$ such that $\Hoo(C)\geq k$.  There is a set $C'$ with $|C'|\ge2^{k-1}$ that  is a $(t, 2\epsilon)$-(maximal error) Shannon code with recovery procedure $\rec$.
\end{lemma}

We can now formalize the intuition above.  A sketch that retains $\tilde{m}$-bits of relaxed HILL entropy implies a good error correcting code with nearly $2^{\tilde{m}}$ points~(proof in \secref{sec:proof of thm sketch implies code}).
\begin{theorem}\label{thm:impSketchArbitraryW}
Let $(\mathcal{M}, \dis)$ be a metric space that is $(s_{sam}, t)$-neighborhood samplable.  Let $(\sketch, \rec)$ be an HILL-entropy $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch that is $(\epsilon, s_{sec})$-secure with error $\delta$.  Let $s_{rec}$ denote the size of the circuit that computes $\rec$.  If $s_{sec}\geq (t(s_{neigh}+s_{rec}))$,  then there exists a value $s$ and a set $C$ with $|C|\geq 2^{\tilde{m}-2}$  that is a $(t, 4(\epsilon+t\delta))$-Shannon code with recovery procedure $\rec(\cdot, s)$.
%Let $W$ be a flat distribution~(all points in the support of $W$ have the same probability) over $\mathcal{M}$ where $\Hoo(W)\geq k$ and   Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$.  If $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $O(s_{neigh}+s_{rec})$, then $\exists x, W'$ where $|W'|\geq |W|/2 \geq 2^{k-1}$ such that $W'$ is a $(t, 2\epsilon)$ Shannon code with recovery procedure $\rec(\cdot, \sketch(x))$.
\end{theorem}
%The code provided in \thref{thm:impSketchArbitraryW} is weaker than a Shannon error correcting code~\cite{shannon1948}.  In a Shannon code, for all codewords $c, \Pr[c'\leftarrow \sample(c) \wedge \rec(c') \neq c]<\epsilon$.  Bounds for this type of code are well known~\cite{shannon1948} and efficient constructions exist~\cite{forney1966}.  Requiring proper decoding for only a random codeword is a significant restriction particularly in the case where the probability of outcomes in $W$ differs significantly~(e.g. where $\exists w_1,w_2\in W$ such that $\Pr[W=w_1]/\Pr[W=w_2] = \ngl$).  However, this is still a meaningful set of error correcting codes.  A similar question is considered in Appendix C of \cite{DBLP:journals/siamcomp/DodisORS08}.  They are able to achieve results for Hamming codes~(as they are not restricted to sampling a polynomial portion of the space)\bnote{expand on this explanation}.

@@

\subsection{Proof of \thref{thm:impSketchArbitraryW}}
\label{sec:proof of thm sketch implies code}
\begin{proof}
  Let $W$ be an arbitrary distribution of min-entropy $m$.  Let $(Y, Z)$ be a joint distribution such that $\Hav(Y | Z)\geq k$ and
\[ 
\delta^{\mathcal{D}_{s_{sec}}}((W, \sketch(W)), (Y, Z))<\epsilon.
\]  
where  $s_{sec} \geq t(s_{neigh}+s_{rec})$.  One such $(Y, Z)$ must exist by the definition of conditional HILL entropy.
%Let $X$ be arbitrarily but independently distributed over $\mathcal{M}$. Let $\delta^D((X, \sketch(X)), (W, \sketch(X)))<\epsilon$ for negligible $\epsilon$ and $D$ of size at least $s=O(s_{neigh}+s_{rec})$.  This implies that $H^{\hill}_{\epsilon, s}(X|\sketch(X))\geq k$.  
Define $D$ as:
\begin{enumerate}
\item Input $y\in\mathcal{M}, z \in\{0, 1\}^*, t$.
\item For all $1\leq t'\leq t$: 
\subitem  $y'\leftarrow \sample(y, t')$.
\subitem If $\rec(y', z) \neq  y$ output $0$.
\item Output $1$.
\end{enumerate}
 By correctness of the sketch $ \Pr[D(W, \sketch(W)) =1]\ge 1-t\delta$.  Since 
$\delta^D((W, \sketch(W)), (Y, Z))<\epsilon$, we know $\Pr[D(Y, Z) = 1]>1-\epsilon-t\delta$.  By Markov's inequality,  there exists a set $S_Z$ such that $\Pr[Z\in S_Z]\ge 1/2$ and for all $z\in S_Z$, $\Pr[ D(Y|z, z) =1]> 1- 2(\epsilon + t\delta)$.  Moreover, by \cite[Lemma 2.2a]{DBLP:journals/siamcomp/DodisORS08} (which is derived simply via Markov's inequality applied to the positive random variable $\max_y \Pr[Y_s=y]$), there exists a set $S'_Z$ such that $\Pr[z\in S'_Z]> 1/2$ and for all $z\in S'_Z$, $\Hoo(Y | z)\ge k-1$. \lnote{simplified this derivation}\bnote{I don't believe this fix}  Fix one value $z \in S_Z\cap S'_Z$ (which exists because the sum of probabilities of $S_Z$ and $S'_Z$ is greater than 1).  
Thus, for all such that $t', 1\leq t'\leq t$, 
\[ \Pr_{y\leftarrow Y|z}[y'\leftarrow \sample(y, t') \wedge \rec(y',s) = y]> 1-2(\epsilon+t\delta).\]  
%Thus, $\rec(\cdot, \sketch(x'))$ is a decoding procedure that succeeds on a random neighbor of a random codeword with probability all but $\epsilon$.  
Thus,  $Y|z$ is a $(t, 2(\epsilon+t\delta))$-average error Shannon code with recovery $\rec(\cdot,s)$ and $2^{k-1}$ points.  The statement of the theorem follows by application of \lemref{lem:averageToMaximalError}.  
\end{proof}

@@

\ignore{
\subsection{Old parameter setting}
The question then becomes whether there is a setting 
Our construction has two goals: 1) maximizing correcting capability~(while retaining polynomial time decoding, and 2) maximizing the unpredictability entropy of $W$ conditioned on the construction~($\tilde{m}$ in \defref{def:comp secure sketch}).  Our parameters will differ significantly depending on what setting of $t$ is used.  We will consider both settings where $t\leq m/n-2$ and $t\leq c\log n (m/n-2)$.  Recall these corresponding to Construction~\ref{cons:decoding algorithm} running either in fixed polynomial time or time approximately $n^{2c}$.  We consider each of these settings:
